Implicit yaddayadda

### 2011-10-11 papers/PLDI2012/implicitization.tex
introduction de la partie experiments

Our analyzer uses Yices \cite{DBLP:conf/cav/DutertreM06}
 or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08} as SMT-solver.
\section{Conclusion}

>>>>

We have implemented our proposed solutions inside a prototype intraprocedural
static analyzer,
as well as the classical abstract interpretation algorithm, and the state-of-the-art
techniques \emph{Path Focusing} \cite{Monniaux_Gonnord_SAS11} and \emph{Guided
Static Analysis} \cite{DBLP:conf/sas/GopanR07}.
We also can choose among different abstract domains: convex polyhedra, octagons,
intervals, grids (convex polyhedra and linear congruences).

For the techniques involving SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08}
as SMT-solver.

We conducted extensive experiments on real-life programs in order to compare the
different techniques. We also compared the precision of the analysis depending
on the choice of the abstract domain.

\section{Conclusion}
